Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-30 doc/JFLA2022/paper.tex
Typo fix and uniformize Coq-community casing.

\begin{abstract}
  \emph{Hydra-battles} is a collaborative library on discrete math, written for the Coq proof assistant, and developped under the \emph{Coq-Community} project. The proof scripts are
  accompanied with an electronic book, made with the help of the \emph{Alectryon} litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must continuously satisfied:
   maintenance of the library with respect to several Coq-Community projects it requires and evolutions of Coq, and 
  consistency of the book with respect to the library. 
\end{abstract}

@@

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-Community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-Community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of former \emph{contribs} Cantor and Additions (under the new names of Hydra-battles and Addition-chains), the Pocklington library, extracted from Russel O'Connor's Goedel \emph{contrib}~\cite{OConnor05, Goedel} and a bridge to the Gaia library (\emph{contrib} of José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

@@

 Prior stages of this project have already been presented at
 JFLA~\cite{PCiota, JFLA2018paper}.
We present recent evolutions of the library: new results, interaction within the Coq-Community project~\cite{CoqCommunity}, and documentation generated with Alectryon~\cite{alectryonpaper, alectryongithub}.

@@

\section{Integration within Coq-Community}

@@

\subsection{Interactions with other Coq-Community projects}

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, we used the formalization of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-Community}.

@@

We plan to extend our libraries in two main directions.
The Gaia project~\cite{Gaia}, also maintained on \textit{Coq-Community} contains a development by José Grimm~\cite{grimm:hal-00911710}. This library is dedicated  to the implementation in \textit{Coq (SSreflect)} of books from  Bourbaki's Elements of Mathematics. It contains data structures which are compatible with our ordinal notations. 
Our plan is to build a  bridge between  the combinatorial results of \textit{hydra-battles} and the set-theoretic content of \textit{Gaia}, and make possible the transfer of theorems between both libraries.
Another direction would be to write in \textit{Coq} a formal proof of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.

>>>>

\begin{abstract}
  \emph{Hydra-battles} is a collaborative library on discrete math, written for the Coq proof assistant, and developed under the \emph{Coq-community} project. The proof scripts are
  accompanied with an electronic book, made with the help of the \emph{Alectryon} litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must continuously satisfied:
   maintenance of the library with respect to several Coq-community projects it requires and evolutions of Coq, and 
  consistency of the book with respect to the library. 
\end{abstract}

@@

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of former \emph{contribs} Cantor and Additions (under the new names of Hydra-battles and Addition-chains), the Pocklington library, extracted from Russel O'Connor's Goedel \emph{contrib}~\cite{OConnor05, Goedel} and a bridge to the Gaia library (\emph{contrib} of José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

@@

 Prior stages of this project have already been presented at
 JFLA~\cite{PCiota, JFLA2018paper}.
We present recent evolutions of the library: new results, interaction within the Coq-community project~\cite{CoqCommunity}, and documentation generated with Alectryon~\cite{alectryonpaper, alectryongithub}.

@@

\section{Integration within Coq-community}

@@

\subsection{Interactions with other Coq-community projects}

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, we used the formalization of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-community}.

@@

We plan to extend our libraries in two main directions.
The Gaia project~\cite{Gaia}, also maintained on \textit{Coq-community} contains a development by José Grimm~\cite{grimm:hal-00911710}. This library is dedicated  to the implementation in \textit{Coq (SSreflect)} of books from  Bourbaki's Elements of Mathematics. It contains data structures which are compatible with our ordinal notations. 
Our plan is to build a  bridge between  the combinatorial results of \textit{hydra-battles} and the set-theoretic content of \textit{Gaia}, and make possible the transfer of theorems between both libraries.
Another direction would be to write in \textit{Coq} a formal proof of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.
